%-------------------------
% Resume in Latex
% Author : Mateo Wang
% Based off of: https://github.com/jakegut/resume
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% Set footskip to minimum recommended value
\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge Mateo Wang} \\ \vspace{1pt}
  % I don't have the phone # link to tel:4089136163 because most PDF viewers don't support it
  \small(408) 913-6163 $|$ \href{mailto:hey@mateowang.dev}{\underline{hey@mateowang.dev}} $|$
  \href{https://linkedin.com/in/mateo-wang}{\underline{linkedin.com/in/mateo-wang}} $|$
  \href{https://github.com/SwiftWinds}{\underline{github.com/SwiftWinds}} $|$
  New York, NY
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer}{Jun. 2025 -- Present}
{Amazon, Inc.}{New York, NY}
\resumeItemListStart
\resumeItem{Maintained and enhanced advertisement management platform powering \textbf{\$3B} in annual publisher revenue}
\resumeItem{Designed AI-powered podcast ad placement tool using AWS Transcribe, Lambda, and Bedrock that reduced ad placement creation time by \textbf{90\%+} and cut advertiser onboarding time by \textbf{60\%}}
\resumeItem{Architected and launched PubTechFeatureFlag, an org-wide Java-based feature flag service adopted by \textbf{4 teams}, eliminating \textbf{300+} hours of redundant development across Publisher Technology organization}
\resumeItem{Participated in \textbf{4 on-call rotations}, resolved critical ad placement bug preventing \textbf{\$20K+} revenue loss}
\resumeItemListEnd

\resumeSubheading
{Founding Engineer}{Aug. 2024 -- Jun. 2025}
{ChipAgents, Inc.}{Santa Barbara, CA}
\resumeItemListStart
\resumeItem{Built landing page w/ advanced anti-spam filtering, generating \textbf{200+} qualified leads in 6 months with \textbf{\textless1\%} spam}
\resumeItem{Developed Next.js web dashboard w/ RBAC for \textbf{50+} active users, reducing customer support inquiries by \textbf{40\%}}
\resumeItem{Streamlined CI/CD pipelines using GitHub Actions, reducing deployment time from \textbf{2 hours} to \textbf{10 minutes}}
\resumeItem{Drove business development at \textbf{5+} industry events, engaging \textbf{100+} qualified leads \& demoing to \textbf{200+} attendees}
\resumeItemListEnd


\resumeSubheading
{Machine Learning Intern}{Jun. 2023 -- Sep. 2023}
{Moloco, Inc.}{Redwood City, CA}
\resumeItemListStart
\resumeItem{Improved ad click-through prediction from \textbf{77\%} to \textbf{85\%}, increasing revenue by estimated \textbf{\$2.1M} annually}
\resumeItem{Doubled training lookback window from 14 to 28 days, improving accuracy by \textbf{17\%} and reducing prediction drift}
\resumeItem{Implemented causal inference pipeline, enabling \textbf{more accurate} attribution modeling for advertisers}
\resumeItem{Utilized first-party data to train an LLM for high-fidelity user embeddings, improving campaign ROI by \textbf{20\%+}}
\resumeItemListEnd

\resumeSubheading
{Software Engineering Intern}{Jun. 2022 -- Dec. 2022}
{Invoca, Inc.}{Santa Barbara, CA}
\resumeItemListStart
\resumeItem{Led and delivered scheduled email attachments feature on time to \textbf{500+} customers, increasing email clicks by \textbf{25\%}}
\resumeItem{Created custom date selector React component adopted across \textbf{15+} dashboard views for \textbf{1K+} daily active users}
\resumeItem{Optimized GraphQL and Ruby backend integration with MySQL database, reducing query latency by \textbf{40\%}}
\resumeItem{Eliminated \textbf{20K+} lines of legacy Backbone.js code during React migration, reducing bug count by \textbf{30\%}}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Data Science Intern}{Jun. 2021 -- Sep. 2021}
{Tascent, Inc.}{Los Gatos, CA}
\resumeItemListStart
\resumeItem{Trained CNN and tuned SVM kernel achieving \textbf{96\%} and
  \textbf{96.5\%} accuracy for low-res thermal motion detection}
\resumeItem{Automated thermal image labeling pipeline, accelerating dataset generation from \textbf{weeks to days}}
\resumeItem{Deployed multi-sensor recording system (RGB/thermal/depth), improving liveness detection accuracy by \textbf{80\%}}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{Oct. 2020 -- Jan. 2021}
{UnMesh, LLC.}{New York, NY}
\resumeItemListStart
\resumeItem{Programmed React Native UI for user profile statistics screen, fetching data with REST API from Node.js backend}
\resumeItem{Migrated deployment from EC2 to microservices with MongoDB Atlas and AWS Lambda, reducing costs by \textbf{60\%}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{UC Santa Barbara}{3.71 GPA $|$ Aug. 2020 -- Jun. 2024}
{Bachelor of Science in Computer Science, Technology Management Certificate}{Santa Barbara, CA}
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: JavaScript, TypeScript, HTML, CSS, Python, SQL, C/C++, Rust, Zig, C\#, Java, Bash, Kotlin, Dart} \\
        \textbf{Frameworks}{: React, Vue, Node.js, Express.js, Tailwind CSS, Firebase, Unity, Arduino, Bootstrap, Svelte} \\
        \textbf{Developer Tools}{: Git, Docker, Kubernetes, Google Cloud Platform, AWS, Azure} \\
        \textbf{Libraries}{: PyTorch, TensorFlow, NumPy, pandas, Matplotlib, FastAPI, Flask, OpenCV, Keras, fast.ai} \\
        }}
\end{itemize}


%-------------------------------------------
\section{Hackathon Awards}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{ShellHacks 2022}{: DAOchow.tech wins 2nd place of 1200+ competitors} \\
        \textbf{HackMIT 2020}{: latent-space.tech wins 3rd place of 1000+ competitors} \\
        \textbf{LAHacks 2020}{: Archiscape wins 1st place of 192 projects} \\
        }}
\end{itemize}

\end{document}
